full title

### 2020-10-29 paper/pldi21/motivation.tex
Fixed error in motivation
Revising Section 2. motivation.

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var args = Array(length - 1),
      array = arguments[0],
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(
    isArray(array) ? copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function.}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) {
  ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load the list of states of the United States.}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option of server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load more Zoom events from the server.}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
  \label{fig:example}
  in \code{zoom.us} site.}
\end{figure}

In this section, we will explain the motivation of the combined analysis for
JavaScript programs with a simple motivating example described in
Figure~\ref{fig:example}.  It shows how to utilize dynamic analysis during
static analysis using lazy concrete execution to increase performance and
precision of static analysis.

For a motivating example, we excerpt the \jscode{concat} function in
Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
the most popular npm package~\footnote{https://www.npmjs.com/browse/depended}
and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
function creates a new array concatenating given arrays or values.  It first
checks the length of arguments in line 2-3. Then, it stores the first argument
to \jscode{array} in line 5 and copies the remaining arguments to \jscode{args} in
line 7-8.  Finally, it creates a new array by copying the given array via
\jscode{copyArray} or initializing with a single value in line 10, and pushes
each element of \jscode{args} after flattening it via \jscode{baseFlatten} in
line 11.

For applications of Lodash, we excerpt two functions \jscode{changeCountry} in
Figure~\ref{fig:changeCountry} and \jscode{getData} in Figure~\ref{fig:getData}
from the \code{zoom.us}~\cite{zoom} site.  The website \code{zoom.us} is
homepage of Zoom, which is a videotelephony software program developed by Zooom
Video Communications and it is ranked as \inred{16th} popular web site accroding
to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var args = Array(length - 1),
      array = arguments[0],
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(
    isArray(array) ? copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function.}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) {
  ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load the list of states of the United States.}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option of server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load more Zoom events from the server.}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
  in \code{zoom.us} site.}
  \label{fig:example}
\end{figure}

In this section, we first point out limitations that existing techniques face to
analyze the real-world example described in Figure~\ref{fig:example}.
We then show how our combined analysis increase the analysis scalability and
precision through lazy concrete execution, seamlessly combined with the original
static analysis.

We excerpt the \jscode{concat} function in Figure~\ref{fig:concat} from Lodash
library~\cite{lodash} (v4.17.20), which is the most popular npm package~\footnote{https://www.npmjs.com/browse/depended}
that \inred{124,562} npm packages depend on.
The \jscode{concat} function creates a new array concatenating given arrays or
values.
It first checks the length of arguments in line 2-3. Then, it stores the first
argument to \jscode{array} in line 5 and copies the remaining arguments to
\jscode{args} in line 7-8.
Finally, it creates a new array by copying the given array via \jscode{copyArray}
or initializing with a single value in line 10, and pushes each element of
\jscode{args} after flattening it via \jscode{baseFlatten} in line 11.

A low degree of context sensitivity tends to face spurious callee explosion
during analyzing \jscode{concat} function.
The analysis is not supposed to lose precision for the loop in line 7-8.
Moreover, \jscode{baseFlatten} has a recursive call in a loop that is a
traditional challenge for static analysis.

We excerpt two functions \jscode{changeCountry} in Figure~\ref{fig:changeCountry}
and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom}
site.
The website \code{zoom.us} is ranked at \inred{16th} popular web site accroding
to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
